The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-31 cordillera-climate.tex
Correct three typos (reviewers)

Most likely, this is the signature of an orographic precipitation effect. As described in Sect.~\ref{sec:climate}, the topography of the Northern American Cordillera is such that its western ranges form a~continuous orographic barrier, causing high precipitation along the Pacific coast while leaving much of the interior arid. However the ability of a~GCM to reproduce these contrasts in precipitation is bounded by spatial resolution. In a~model of coarser resolution, these high mountain ranges are reduced to smooth hills and the modelled distribution of precipitation is also smoother (Fig.~\ref{fig:oroprecip}). However, this effect alone cannot explain the widespread and pronounced positive precipitation anomalies observed in CFSR data (Figs.~\ref{fig:precheatmap} and \ref{fig:precdiff}) despite of its high spatial resolution (Table~\ref{tab:reanalyses}).

@@

% fig:tempheatmap
\begin{figure}
  \includegraphics{cordillera-climate-tempheatmap}
  \caption{Density maps showing a~comparison of summer (JJA) surface air temperature data from the WorldClim climatology, against that of each reanalysis. Climate data are presented after bilinear spatial interpolation and correction for topographic differences to WorldClim data, using a lapse rate of 6\,\unit{{\degree}C\,km^{-1}}. Colour mapping is based on a~logarythmic scale. Note the cold bias of NCEP/NCAR data relative to WorldClim data.}
  \label{fig:tempheatmap}
\end{figure}

@@

% fig:precheatmap
\begin{figure}
  \includegraphics{cordillera-climate-precheatmap}
  \caption{Density maps showing a~comparison of winter (DJF) precipitation rate from the WorldClim climatology, against that of each reanalysis, after bi-linear spatial interpolation. Colour mapping is based on a~logarythmic scale. Note the wet bias of all reanalysis data relative to WorldClim data.}
  \label{fig:precheatmap}
\end{figure}

>>>>

Most likely, this is the signature of an orographic precipitation effect. As described in Sect.~\ref{sec:climate}, the topography of the Northern American Cordillera is such that its western ranges form a~continuous orographic barrier, causing high precipitation along the Pacific coast while leaving much of the interior arid. However the ability of a~GCM to reproduce these contrasts in precipitation is bounded by spatial resolution. In a~model of coarser resolution, these high mountain ranges are reduced to smooth hills and the modelled distribution of precipitation is also smoother (Fig.~\ref{fig:oroprecip}). However, this effect alone cannot explain the widespread and pronounced positive precipitation anomalies observed in CFSR data (Figs.~\ref{fig:precheatmap} and \ref{fig:precdiff}) despite its high spatial resolution (Table~\ref{tab:reanalyses}).

@@

% fig:tempheatmap
\begin{figure}
  \includegraphics{cordillera-climate-tempheatmap}
  \caption{Density maps showing a~comparison of summer (JJA) surface air temperature data from the WorldClim climatology, against that of each reanalysis. Climate data are presented after bilinear spatial interpolation and correction for topographic differences to WorldClim data, using a lapse rate of 6\,\unit{{\degree}C\,km^{-1}}. Colour mapping is based on a~logarithmic scale. Note the cold bias of NCEP/NCAR data relative to WorldClim data.}
  \label{fig:tempheatmap}
\end{figure}

@@

% fig:precheatmap
\begin{figure}
  \includegraphics{cordillera-climate-precheatmap}
  \caption{Density maps showing a~comparison of winter (DJF) precipitation rate from the WorldClim climatology, against that of each reanalysis, after bi-linear spatial interpolation. Colour mapping is based on a~logarithmic scale. Note the wet bias of all reanalysis data relative to WorldClim data.}
  \label{fig:precheatmap}
\end{figure}
